---
title: "Mod 2 Evaluation"
author: "Tom Zhang"
date: "6/8/2020"
output: html_document
---

## fitting mod2v2
## trophies ~ day + card indicators + card numeric level + (card numeric level)^2 + card interactions
```{r}
# import data
library(tidyverse)
library(broom)
cr_s3_df_ind_left <- read_csv("data/cr_s3_df_ind_left.csv")

# cleaning up data
df_mod2 <-
  cr_s3_df_ind_left %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth, 27:214)

# mod_cardInt: trophies ~ cards + all 2-way card interactions
df_cardInt <-
  df_mod2 %>%
    select(1, 3:96)

t1_start <- Sys.time()
mod_cardInt <- lm(leftstartingtrophies ~ (.)^2, data = df_cardInt) # all 2-way interactions (7 min)
t1_end <- Sys.time()
t1_end - t1_start

# mod2v2
f2 <- as.formula(
  paste(
    "leftstartingtrophies ~",
    paste(
      c(
        paste('`', names(df_mod2)[2:190], '`', sep = ''), # day + cards + levels
        paste('I(`', names(df_mod2)[97:190], '`^2)', sep = ''), # quadratic levels
        names(coef(mod_cardInt))[-1:-95] # all 2-way card interactions
        ),
      collapse = " + "
      )
    )
  )

t2_start <- Sys.time()
mod2v2 <- lm(formula = f2, data = df_mod2) # 7 min
t2_end <- Sys.time()
t2_end - t2_start


#summary(mod2v2)
tidy(mod2v2)
glance(mod2v2)
```


## Import/process right deck
```{r}
cr_s3_df_ind_right <- read_csv("data/cr_s3_df_ind_right.csv")

df_mod2_right <-
  cr_s3_df_ind_right %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(rightstartingtrophies, dayOfTheMonth, 27:214)
```


# Predicting right deck trophies using mod2v2 (i.e., created from left deck)
```{r}
t3_start <- Sys.time()

df_mod2v2_aug <-
  df_mod2_right %>%
    augment(mod2v2, data = .) %>%
    select(1, 191:196)

t3_end <- Sys.time() # about 56 min
t3_end - t3_start

df_mod2v2_aug # comparing observed and fitted for right deck
```


## save prediction df
```{r}
write_csv(df_mod2v2_aug, "data/df_mod2v2_aug.csv")
```








# Using biglm for mod2v2 - Use this for predictions

## fitting mod2v2_biglm
## trophies ~ day + card indicators + card numeric level + (card numeric level)^2 + card interactions
```{r}
# import data
library(tidyverse)
library(broom)
library(biglm)
cr_s3_df_ind_left <- read_csv("data/cr_s3_df_ind_left.csv")

# cleaning up data
df_mod2 <-
  cr_s3_df_ind_left %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth, 27:214, -Zappies)

# mod_cardInt: trophies ~ cards + all 2-way card interactions
df_cardInt <-
  df_mod2 %>%
    select(1, 3:95)

fInt <- as.formula(
  paste(
    "leftstartingtrophies ~ (",
    paste(
      paste("`", names(df_cardInt)[-1], "`", sep = ""),
      collapse = " + "
    ),
    ")^2"
  )
)

t1_start <- Sys.time()
mod_cardInt_biglm <- biglm::biglm(formula = fInt, data = df_cardInt)
t1_end <- Sys.time()
t1_end - t1_start # 4 min

# mod2v2
f2_biglm <- as.formula(
  paste(
    "leftstartingtrophies ~",
    paste(
      c(
        paste('`', names(df_mod2)[2:189], '`', sep = ''), # day + cards + levels
        paste('I(`', names(df_mod2)[96:189], '`^2)', sep = ''), # quadratic levels
        mod_cardInt_biglm$names[-1:-94] # all 2-way card interactions
        ),
      collapse = " + "
      )
    )
  )

t2_start <- Sys.time()
mod2v2_biglm <- biglm::biglm(formula = f2_biglm, data = df_mod2)
t2_end <- Sys.time()
t2_end - t2_start # 4 min

#summary(mod2v2_biglm)
tidy(mod2v2_biglm)
```


## fitting mod2v2_biglm by blocks of data
## build X matrix for mod2v2_biglm
## trophies ~ day + card indicators + card numeric level + (card numeric level)^2 + card interactions
```{r}
library(tidyverse)
library(broom)
library(biglm)
cr_s3_df_ind_left <- read_csv("data/cr_s3_df_ind_left.csv")

# cleaning up data
df_mod2 <-
  cr_s3_df_ind_left %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth, 27:214)

# card numeric level squared
lvl <-
  df_mod2 %>%
    select(97:190)

lvl_Sq <-
  lvl^2

names(lvl_Sq) <- paste(names(lvl_Sq), "Sq")

# card interactions
cards <-
  df_mod2 %>%
    select(3:96)

cardsIntMTX <- model.matrix(~(.)^2,cards)
cardsIntMTX <- cardsIntMTX[,96:4466]

# combine to create matrix X
X <- cbind(data.matrix(df_mod2[,-1]), data.matrix(lvl_Sq), cardsIntMTX)

# extract Y the response
Y <- data.matrix(df_mod2[,1])



# number of chunks to divide the data into
nChunks <- 10
n <- nrow(df_mod2)
chunkLength <- n / nChunks

# First fit
t_start <- Sys.time()
# using the ith chunk when i = 1
Yi <- matrix(Y[1:chunkLength,])
colnames(Yi) <- "leftstartingtrophies"
Xi <- X[1:chunkLength,]

mod2v2_biglm <- biglm::biglm(Yi ~ Xi, data = data.frame(Yi, Xi))

# Update fit
pb <- txtProgressBar(style = 3)

for (i in 2:nChunks) {
  # reading the i-th chunk of data
  Yi <- matrix(Y[(nrow(Yi) + 1):(nrow(Yi) + chunkLength),])
  colnames(Yi) <- "leftstartingtrophies"
  Xi <- X[(nrow(Yi) + 1):(nrow(Yi) + chunkLength),]

  # Update the fit
  mod2v2_biglm <- update(mod2v2_biglm, moredata = data.frame(Yi, Xi))

  # Progress
  setTxtProgressBar(pb = pb, value = i / nChunks)
}

t_end <- Sys.time()
t_end - t_start

# Final model
summary(mod2v2_biglm)
```


## no blocks - fit all at once
```{r}
library(tidyverse)
library(broom)
library(biglm)
cr_s3_df_ind_left <- read_csv("data/cr_s3_df_ind_left.csv")

# cleaning up data
df_mod2 <-
  cr_s3_df_ind_left %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth, 27:214)

# card numeric level squared
lvl <-
  df_mod2 %>%
    select(97:190)

lvl_Sq <-
  lvl^2

names(lvl_Sq) <- paste(names(lvl_Sq), "Sq")

# card interactions
cards <-
  df_mod2 %>%
    select(3:96)

cardsIntMTX <- model.matrix(~(.)^2,cards)
cardsIntMTX <- cardsIntMTX[,96:4466]

# combine to create matrix X
X <- cbind(data.matrix(df_mod2[,-1]), data.matrix(lvl_Sq), cardsIntMTX)

# extract Y the response
Y <- data.matrix(df_mod2[,1])

# fit
t_start <- Sys.time()
mod2v2_biglm <- biglm::biglm(Y ~ X, data = data.frame(Y, X))
t_end <- Sys.time()
t_end - t_start

tidy(mod2v2_biglm)
```










## Import/process right deck
```{r}
cr_s3_df_ind_right <- read_csv("data/cr_s3_df_ind_right.csv")

df_mod2_right <-
  cr_s3_df_ind_right %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    mutate(leftstartingtrophies = rightstartingtrophies) %>%
    select(leftstartingtrophies, dayOfTheMonth, 27:214, -Zappies)
```


## Predicting right deck trophies using mod2v2_biglm (i.e., created from left deck)
```{r}
t3_start <- Sys.time()


predict(mod2v2_biglm, newdata = df_mod2[1,])


t3_end <- Sys.time() # about 56 min
t3_end - t3_start
```






## evaluation: predicted R^2
```{r}
df_mod2v2_aug <- read_csv("data/df_mod2v2_aug.csv")
```

```{r}
# predictive R-squared = [1 - (PRESS / sums of squares total)] * 100
# predicted residual sums of squares (PRESS)
PRESS <- sum(df_mod2v2_aug$.resid)^2

# slunova
slunova=function(model){
  numpred=model$rank-1
  dferror=df.residual(model)
  dfmodel=numpred
  dftotal=dfmodel+dferror
  sse=sum(model$residual^2)
  ssmodel=sum(model$effects[2:(numpred+1)]^2)
  sstotal=ssmodel+sse
  msmodel=ssmodel/dfmodel
  mse=sse/dferror
  fstat=msmodel/mse
  pvalue=1-pf(fstat,dfmodel,dferror)
  df=c(dfmodel,dferror,dftotal)
  ss=c(ssmodel,sse,sstotal)
  ms=c(msmodel,mse,0)
  f=c(fstat,0,0)
  p=c(pvalue,0,0)
  table=data.frame(df,ss,ms,f,p)
  table[2,4:5]=NA
  table[3,3:5]=NA

colnames(table)=c("Df","Sum Sq","Mean Sq","F value","P(>F)")
  row.names(table)=c("Model","Error","Total")
  class(table)=c("anova","data.frame")
  structure(table,
            heading=c("ANOVA Table",                            paste("Model:", formula(model)[2],formula(model)[1],formula(model)[3],"\n")))
}

slunova(mod2v2)

SSTotal <- 19999

# predicted R^2
predRSq <- 1 - (PRESS / SSTotal)
predRSq
```

```{r}
glance(mod2v2)
```

## plot of residual vs y
```{r}
df_mod2v2_aug %>%
  ggplot(., aes(y = .resid, x = rightstartingtrophies)) +
  geom_point() +
  geom_smooth()
```


# Predicting left deck trophies using mod2v2 (i.e., created from left deck)
```{r}
t3_start <- Sys.time()

df_mod2v2_aug_left <-
  df_mod2 %>%
    augment(mod2v2, data = .) %>%
    select(1, 191:196)

t3_end <- Sys.time() # about 56 min
t3_end - t3_start

df_mod2v2_aug_left # comparing observed and fitted for right deck
```


## save prediction df
```{r}
write_csv(df_mod2v2_aug_left, "data/df_mod2v2_aug_left.csv")
```


## compare left and right deck
```{r}
df1 <-
  df_mod2v2_aug_left %>%
  select(1,4) %>%
  mutate(group = "left")
names(df1)[1] <- "trophies"

df2 <-
  df_mod2v2_aug %>%
  select(1,4) %>%
  mutate(group = "right")
names(df2)[1] <- "trophies"

df3 <- bind_rows(df1, df2)

df3 %>%
  ggplot(., aes(x = trophies, y = .resid, color = group)) +
  geom_point() +
  geom_smooth()
```







## testing predict() for biglm
## whether a random response column will work
```{r}
library(tidyverse)
library(biglm)
iris

modTest <- biglm(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width + Species, data = iris)
summary(modTest)

df_test <-
  iris %>%
    slice(1:5)

predict(modTest, newdata = df_test)

df_test2 <-
  iris %>%
    slice(1:5) %>%
    mutate(Sepal.Length = 10000000000)

predict(modTest, newdata = df_test2) # random values for the response column works
```
















