---
title: "CR_Mod1"
author: "Tom Zhang"
date: "5/19/2020"
output: html_document
---
## Note: subseted data - 2000 cases with indicators (see line 222) - took 15 min to run

## Importing cr card info data
```{r}
library(jsonlite)
library(tidyverse)
cr_cards_list <- fromJSON("clash_royale_season3/clash_royale_card_info.json")
cr_cards_flat <- flatten(cr_cards_list)
cr_cards_df <- as.tibble(cr_cards_flat)
```


## Importing cr matches data
```{r}
library(DBI)

# connect to db
con <- dbConnect(drv=RSQLite::SQLite(), dbname="clash_royale_season3/cr_season3_subset.sqlite")

# list all tables
tables <- dbListTables(con)

# exclude sqlite_sequence (contains table information)
tables <- tables[tables != "sqlite_sequence"]

cr_s3_list <- vector("list", length=length(tables))

# create a data.frame for each table
for (i in seq(along=tables)) {
  cr_s3_list[[i]] <- dbGetQuery(conn=con, statement=paste("SELECT * FROM '", tables[[i]], "'", sep=""))
}

# from list to data frame
library(tidyverse)
cr_s3_flat <- flatten(cr_s3_list)
cr_s3_df <- as_tibble(cr_s3_flat)

# disconnect from database
dbDisconnect(con)
```


## Cleaning up cr matches data & implementing level adjustment
```{r}
cr_s3_df_lvlAdj <-
# card / level separation
cr_s3_df %>%
  mutate(
    leftdeck = str_remove_all(leftdeck, "[\\[\\]\"]"),
    rightdeck = str_remove_all(rightdeck, "[\\[\\]\"]"),
    leftdeckCopy = leftdeck,
    rightdeckCopy = rightdeck
    ) %>%
  separate(leftdeck, sep = ", ", into = c("leftCard1", "leftLvl1", "leftCard2", "leftLvl2", "leftCard3", "leftLvl3", "leftCard4", "leftLvl4", "leftCard5", "leftLvl5", "leftCard6", "leftLvl6", "leftCard7", "leftLvl7", "leftCard8", "leftLvl8")) %>%
  separate(rightdeck, sep = ", ", into = c("rightCard1", "rightLvl1", "rightCard2", "rightLvl2", "rightCard3", "rightLvl3", "rightCard4", "rightLvl4", "rightCard5", "rightLvl5", "rightCard6", "rightLvl6", "rightCard7", "rightLvl7", "rightCard8", "rightLvl8")) %>%

# adding corresponding rarity info




# for left deck
  mutate(
    leftdeckCopy = str_remove_all(leftdeckCopy, ",\\s[:digit:]+"),

# addressing a few conflicts:
# Cannon, Cannon Cart, Giant, Giant Skeleton, Giant Snowball, Goblin Giant, Royal Giant, Goblins, Spear Goblins, Golem, Ice Golem, Wizard, Ice Wizard, Electro Wizard, Knight, Mega Knight, P.E.K.K.A, Mini P.E.K.K.A, Witch, Night Witch, Prince, Dark Prince, Princess, Musketeer, Three Musketeers, Zap, Zappies

# including cards not in the cr_cards_df dataset:
# *Heal, *Heal Spirit, *Battle Healer, *Elixir Golem
    leftdeckCopy = str_replace_all(leftdeckCopy, "Giant Snowball|Royal Giant|Spear Goblins", "Common"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Ice Golem|Mini P.E.K.K.A|Three Musketeers|Zappies|Heal Spirit|Battle Healer|Elixir Golem", "Rare"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Cannon Cart|Giant Skeleton|Goblin Giant|Dark Prince", "Epic"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Ice Wizard|Electro Wizard|Mega Knight|Night Witch|Princess", "Legendary"),
    
# the four rarity categories - according to cr_cards_df

# and cards not in the cr_cards_df dataset
# Fisherman, *Heal changed to Heal Spirit, *Elixir Golem, *Battle Healer, Firecracker, Royal Delivery
    leftdeckCopy = str_replace_all(leftdeckCopy, "Knight|Archers|Goblins|Minions|Barbarians|Skeletons|Bomber|Spear Goblins|Minion Horde|Royal Giant|Ice Spirit|Fire Spirits|Goblin Gang|Elite Barbarians|Royal Recruits|Bats|Rascals|Skeleton Barrel|Cannon|Mortar|Tesla|Arrows|Zap|Giant Snowball|Firecracker|Royal Delivery", "Common"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Giant|Valkyrie|Musketeer|Wizard|Mini P.E.K.K.A|Hog Rider|Three Musketeers|Battle Ram|Ice Golem|Mega Minion|Dart Goblin|Zappies|Flying Machine|Royal Hogs|Goblin Hut|Inferno Tower|Bomb Tower|Barbarian Hut|Elixir Collector|Tombstone|Furnace|Goblin Cage|Fireball|Rocket|Earthquake|Heal", "Rare"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "P.E.K.K.A|Balloon|Witch|Golem|Skeleton Army|Baby Dragon|Prince|Giant Skeleton|Guards|Dark Prince|Bowler|Hunter|Executioner|Cannon Cart|Wall Breakers|Goblin Giant|Electro Dragon|X-Bow|Rage|Goblin Barrel|Freeze|Mirror|Lightning|Poison|Tornado|Clone|Barbarian Barrel", "Epic"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Ice Wizard|Princess|Lava Hound|Miner|Sparky|Lumberjack|Inferno Dragon|Electro Wizard|Bandit|Night Witch|Royal Ghost|Ram Rider|Mega Knight|Magic Archer|Graveyard|The Log|Fisherman", "Legendary"),

# match rarity info with level adjustment
    leftdeckCopy = str_replace_all(leftdeckCopy, "Common", "0"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Rare", "2"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Epic", "5"),
    leftdeckCopy = str_replace_all(leftdeckCopy, "Legendary", "8")
  ) %>%

# separating level adjustment
  separate(leftdeckCopy, sep = ", ", into = c("leftLvlAdj1", "leftLvlAdj2", "leftLvlAdj3", "leftLvlAdj4", "leftLvlAdj5", "leftLvlAdj6", "leftLvlAdj7", "leftLvlAdj8")) %>%

# first transform all levels and their adjustments to numeric rather than character
  mutate(
    leftLvl1 = parse_integer(leftLvl1),
    leftLvl2 = parse_integer(leftLvl2),
    leftLvl3 = parse_integer(leftLvl3),
    leftLvl4 = parse_integer(leftLvl4),
    leftLvl5 = parse_integer(leftLvl5),
    leftLvl6 = parse_integer(leftLvl6),
    leftLvl7 = parse_integer(leftLvl7),
    leftLvl8 = parse_integer(leftLvl8),
    leftLvlAdj1 = parse_integer(leftLvlAdj1),
    leftLvlAdj2 = parse_integer(leftLvlAdj2),
    leftLvlAdj3 = parse_integer(leftLvlAdj3),
    leftLvlAdj4 = parse_integer(leftLvlAdj4),
    leftLvlAdj5 = parse_integer(leftLvlAdj5),
    leftLvlAdj6 = parse_integer(leftLvlAdj6),
    leftLvlAdj7 = parse_integer(leftLvlAdj7),
    leftLvlAdj8 = parse_integer(leftLvlAdj8)
  ) %>%

# now add left card levels with their corresponding adjustments
  mutate(
    leftAdjLvl1 = leftLvl1 + leftLvlAdj1, # adjusted level = original level + level adjustment
    leftAdjLvl2 = leftLvl2 + leftLvlAdj2,
    leftAdjLvl3 = leftLvl3 + leftLvlAdj3,
    leftAdjLvl4 = leftLvl4 + leftLvlAdj4,
    leftAdjLvl5 = leftLvl5 + leftLvlAdj5,
    leftAdjLvl6 = leftLvl6 + leftLvlAdj6,
    leftAdjLvl7 = leftLvl7 + leftLvlAdj7,
    leftAdjLvl8 = leftLvl8 + leftLvlAdj8
  ) %>%




# now do exactly the same thing for the right deck
  mutate(
    rightdeckCopy = str_remove_all(rightdeckCopy, ",\\s[:digit:]+"),

# addressing a few conflicts:
# Cannon, Cannon Cart, Giant, Giant Skeleton, Giant Snowball, Goblin Giant, Royal Giant, Goblins, Spear Goblins, Golem, Ice Golem, Wizard, Ice Wizard, Electro Wizard, Knight, Mega Knight, P.E.K.K.A, Mini P.E.K.K.A, Witch, Night Witch, Prince, Dark Prince, Princess, Musketeer, Three Musketeers, Zap, Zappies

# including cards not in the cr_cards_df dataset:
# *Heal, *Heal Spirit, *Battle Healer, *Elixir Golem
    rightdeckCopy = str_replace_all(rightdeckCopy, "Giant Snowball|Royal Giant|Spear Goblins", "Common"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Ice Golem|Mini P.E.K.K.A|Three Musketeers|Zappies|Heal Spirit|Battle Healer|Elixir Golem", "Rare"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Cannon Cart|Giant Skeleton|Goblin Giant|Dark Prince", "Epic"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Ice Wizard|Electro Wizard|Mega Knight|Night Witch|Princess", "Legendary"),
    
# the four rarity categories - according to cr_cards_df

# and cards not in the cr_cards_df dataset
# Fisherman, *Heal changed to Heal Spirit, *Elixir Golem, *Battle Healer, Firecracker, Royal Delivery
    rightdeckCopy = str_replace_all(rightdeckCopy, "Knight|Archers|Goblins|Minions|Barbarians|Skeletons|Bomber|Spear Goblins|Minion Horde|Royal Giant|Ice Spirit|Fire Spirits|Goblin Gang|Elite Barbarians|Royal Recruits|Bats|Rascals|Skeleton Barrel|Cannon|Mortar|Tesla|Arrows|Zap|Giant Snowball|Firecracker|Royal Delivery", "Common"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Giant|Valkyrie|Musketeer|Wizard|Mini P.E.K.K.A|Hog Rider|Three Musketeers|Battle Ram|Ice Golem|Mega Minion|Dart Goblin|Zappies|Flying Machine|Royal Hogs|Goblin Hut|Inferno Tower|Bomb Tower|Barbarian Hut|Elixir Collector|Tombstone|Furnace|Goblin Cage|Fireball|Rocket|Earthquake|Heal", "Rare"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "P.E.K.K.A|Balloon|Witch|Golem|Skeleton Army|Baby Dragon|Prince|Giant Skeleton|Guards|Dark Prince|Bowler|Hunter|Executioner|Cannon Cart|Wall Breakers|Goblin Giant|Electro Dragon|X-Bow|Rage|Goblin Barrel|Freeze|Mirror|Lightning|Poison|Tornado|Clone|Barbarian Barrel", "Epic"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Ice Wizard|Princess|Lava Hound|Miner|Sparky|Lumberjack|Inferno Dragon|Electro Wizard|Bandit|Night Witch|Royal Ghost|Ram Rider|Mega Knight|Magic Archer|Graveyard|The Log|Fisherman", "Legendary"),

# match rarity info with level adjustment
    rightdeckCopy = str_replace_all(rightdeckCopy, "Common", "0"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Rare", "2"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Epic", "5"),
    rightdeckCopy = str_replace_all(rightdeckCopy, "Legendary", "8")
  ) %>%

# separating level adjustment
  separate(rightdeckCopy, sep = ", ", into = c("rightLvlAdj1", "rightLvlAdj2", "rightLvlAdj3", "rightLvlAdj4", "rightLvlAdj5", "rightLvlAdj6", "rightLvlAdj7", "rightLvlAdj8")) %>%

# first transform all levels and their adjustments to numeric rather than character
  mutate(
    rightLvl1 = parse_integer(rightLvl1),
    rightLvl2 = parse_integer(rightLvl2),
    rightLvl3 = parse_integer(rightLvl3),
    rightLvl4 = parse_integer(rightLvl4),
    rightLvl5 = parse_integer(rightLvl5),
    rightLvl6 = parse_integer(rightLvl6),
    rightLvl7 = parse_integer(rightLvl7),
    rightLvl8 = parse_integer(rightLvl8),
    rightLvlAdj1 = parse_integer(rightLvlAdj1),
    rightLvlAdj2 = parse_integer(rightLvlAdj2),
    rightLvlAdj3 = parse_integer(rightLvlAdj3),
    rightLvlAdj4 = parse_integer(rightLvlAdj4),
    rightLvlAdj5 = parse_integer(rightLvlAdj5),
    rightLvlAdj6 = parse_integer(rightLvlAdj6),
    rightLvlAdj7 = parse_integer(rightLvlAdj7),
    rightLvlAdj8 = parse_integer(rightLvlAdj8)
  ) %>%

# now add left card levels with their corresponding adjustments
  mutate(
    rightAdjLvl1 = rightLvl1 + rightLvlAdj1, # adjusted level = original level + level adjustment
    rightAdjLvl2 = rightLvl2 + rightLvlAdj2,
    rightAdjLvl3 = rightLvl3 + rightLvlAdj3,
    rightAdjLvl4 = rightLvl4 + rightLvlAdj4,
    rightAdjLvl5 = rightLvl5 + rightLvlAdj5,
    rightAdjLvl6 = rightLvl6 + rightLvlAdj6,
    rightAdjLvl7 = rightLvl7 + rightLvlAdj7,
    rightAdjLvl8 = rightLvl8 + rightLvlAdj8
  ) %>%




# finally, select the columns we need / clean up dataset
  select(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 63, 12, 64, 14, 65, 16, 66, 18, 67, 20, 68, 22, 69, 24, 70, 26, 27, 28, 29, 30, 31, 71, 33, 72, 35, 73, 37, 74, 39, 75, 41, 76, 43, 77, 45, 78))

# now, keep only left deck information
cr_s3_df_lvlAdj_left <-
cr_s3_df_lvlAdj %>%
  select(1:25)

cr_s3_df_lvlAdj_left
```


## Creating indicator variables for cards and levels
```{r}
# first experiment with only a subset df
df1 <-
  cr_s3_df_lvlAdj_left %>%
  select(c(1, 10:25)) #%>%
  #slice(1:200) # only the first few rows

# cleaning up cards with separate_rows()
deck <- 
  df1 %>%
    unite(c(2, 4, 6, 8, 10, 12, 14, 16), col = "card", sep = ", ") %>%
    separate_rows(card, sep = ", ") %>%
    select(1:2)

# preparing level column
lvl <-
  df1 %>%
    unite(c(3, 5, 7, 9, 11, 13, 15, 17), col = "lvl", sep = ", ") %>%
    separate_rows(lvl, sep = ", ") %>%
    select(3)

lvl <- bind_cols(deck, lvl)

# creating indicator variables for cards
deck$card <- factor(deck$card)
dummies <- model.matrix(~ -1 + deck$card)

deck <- bind_cols(deck, as_data_frame(dummies))

names(deck) = str_remove_all(names(deck), "deck\\$card")

deck <- 
  deck %>%
  group_by(id) %>%
  mutate_if(is.numeric, sum)

deck

# dummies for levels
lvl <- unite(lvl, -1, col = "cardLvl", sep = ", ")

lvl$cardLvl <- factor(lvl$cardLvl)
dummies <- model.matrix(~ -1 + lvl$cardLvl)

lvl <- bind_cols(lvl, as_data_frame(dummies))

names(lvl) <- str_remove_all(names(lvl), "lvl\\$cardLvl|\\.|,\\s|-") # important!!! for parse_number()

lvl <- 
  lvl %>%
  group_by(id) %>%
  mutate_if(is.numeric, sum) %>%
  select(-2) %>%
  group_by(id) %>%
  slice(1)

lvl
```


## Transforming card level indicators into actual levels - time consuming
### Took 50 sec to run 200 original cases
### Took 15 min to run 2000 original cases
```{r}
# start timer
start_time <- Sys.time()



# replace 1's with column name, which is card & level
for (y in 2:ncol(lvl)) {
  lvl[[y]] = as.character(lvl[[y]])
  for (x in 1:nrow(lvl)) {
    if (lvl[x,y] == "1") {
      lvl[x,y] = names(lvl)[y]
    }
  }
}



# stop timer
end_time <- Sys.time()

# drop card names; keep only the card levels
lvl <-
  lvl %>%
    mutate_if(is.character, parse_number)

# merge all columns representing the same card, but different levels
lvl <-
  lvl %>%
    gather(-1, key = "cards", value = "level") %>%
    mutate(cards = str_remove_all(cards, "[:digit:]")) %>%
    group_by(id, cards) %>%
    summarise(level = sum(level)) %>%
    spread(cards, level)

names(lvl) <- paste(names(lvl), "Lvl")
names(lvl)[1] <- "id"

lvl

# time elapsed
end_time - start_time
```


## Merge deck df and level df
```{r}
deck <-
  deck %>%
    select(-2) %>%
    group_by(id) %>%
    slice(1)

deckLvl <- left_join(deck, lvl, by = "id")

deckLvl
```


## Join cleaned original df with deck/lvl df for only left deck
```{r}
cr_s3_df_ind_left <- left_join(cr_s3_df_lvlAdj_left, deckLvl, by = "id")
cr_s3_df_ind_left
```


## Saving fianl df
```{r}
write_csv(cr_s3_df_ind_left, path = "data/cr_s3_df_ind_left.csv")
```


## Building model

Goal:
logistic regression model
  predict win rate based on
    cards used in a player’s deck
    level of their cards
    trophy level of the player

Simplified version:
using linear regression to model trophies
  cards used in a player’s deck
  level of their cards

```{r}
cr_s3_df_ind_left <- read_csv("data/cr_s3_df_ind_left.csv")
```

```{r}
df_mod1 <-
  cr_s3_df_ind_left %>%
    select(-1:-5) %>%
    select(-2:-20)

mod1 <- lm(leftstartingtrophies ~ ., data = df_mod1)
summary(mod1)
```






















