---
title: "CR_Mod2"
author: "Tom Zhang"
date: "5/25/2020"
output: html_document
---

## Importing data for linear regression model
```{r}
library(tidyverse)
library(broom)
library(biglm)
cr_s3_df_ind_left <- read_csv("data/cr_s3_df_ind_left.csv")
```


## mod_day: trophies ~ day of the month
```{r}
df_day <-
  cr_s3_df_ind_left %>%
    select(leftstartingtrophies, battletime) %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth)

mod_day <- lm(leftstartingtrophies ~ dayOfTheMonth, data = df_day)
summary(mod_day)
```


## mod_day0: trophies ~ day of the month (but with < 4000 trophies - arena 1-12)
```{r}
df_day0 <-
  cr_s3_df_ind_left %>%
    filter(leftstartingtrophies < 4000) %>%
    select(leftstartingtrophies, battletime) %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth)

mod_day0 <- lm(leftstartingtrophies ~ dayOfTheMonth, data = df_day0)
summary(mod_day0)
```

```{r}
# trophies vs dayOfTheMonth plot for < 4000 trophies
df_day0 %>%
  ggplot(., aes(x = dayOfTheMonth, y = leftstartingtrophies)) +
  geom_point() +
  geom_smooth(method = "loess", color = "blue") +
  geom_smooth(method = "lm", color = "red") +
  labs(
    x = "Day of the Month",
    y = "Left Starting Trophies",
    title = "Scatterplot of Trophies vs Day of the Month for Arena 1-12 Matches\n(< 4000 Trophies)"
  ) +
  theme_bw()
```




## mod_day4000: trophies ~ day of the month (but with only 4000+ trophies - arena 13)
```{r}
# list of arena id in this df
# 54000014 = Challenger III
# arena 13 indicator?
sort(unique(cr_s3_df_ind_left$arenaid))
```

```{r}
df_day4000 <-
  cr_s3_df_ind_left %>%
    filter(leftstartingtrophies >= 4000) %>%
    select(leftstartingtrophies, battletime) %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth)

mod_day4000 <- lm(leftstartingtrophies ~ dayOfTheMonth, data = df_day4000)
summary(mod_day4000)
```

```{r}
# trophies vs dayOfTheMonth plot for 4000+ trophies
df_day4000 %>%
  ggplot(., aes(x = dayOfTheMonth, y = leftstartingtrophies)) +
  geom_point() +
  geom_smooth(method = "loess", color = "blue") +
  geom_smooth(method = "lm", color = "red") +
  labs(
    x = "Day of the Month",
    y = "Left Starting Trophies",
    title = "Scatterplot of Trophies vs Day of the Month for Arena 13 Matches\n(4000+ Trophies)"
  ) +
  theme_bw()
```




## mod_day4000_biglm: Using biglm for mod_day4000
```{r}
mod_day4000_biglm <- biglm::biglm(leftstartingtrophies ~ dayOfTheMonth, data = df_day4000)
summary(mod_day4000_biglm)
# compare with lm()
print("-----")
summary(mod_day4000)
```




## Cleaning up data for mod2v1
```{r}
df_mod2 <-
  cr_s3_df_ind_left %>%
    mutate(battletime = as.character(as.POSIXct(battletime, origin="2019-09-02", tz="GMT"))) %>%
    mutate(battletime = str_remove(battletime, "\\s.*")) %>%
    separate(battletime, into = c("yearMonth", "dayOfTheMonth"), sep = -2) %>%
    mutate(dayOfTheMonth = as.numeric(dayOfTheMonth)) %>%
    select(leftstartingtrophies, dayOfTheMonth, 27:214)
```


## mod2v1: trophies ~ day + card indicators + card numeric level + (card numeric level)^2
```{r}
f1 <- as.formula(
  paste(
    "leftstartingtrophies ~",
    paste(
      c(
        paste('`', names(df_mod2)[2:190], '`', sep = ''), # day + cards + levels
        paste('I(`', names(df_mod2)[97:190], '`^2)', sep = '') # quadratic levels
        ),
      collapse = " + "
      )
    )
  )

mod2v1 <- lm(formula = f1, data = df_mod2)
#summary(mod2v1)
#names(coef(mod2v1))

#tidy(mod2v1) # coefficients
#glance(mod2v1) # goodness of fit summary
```


## mod_cardInt: trophies ~ cards + all 2-way card interactions
```{r}
df_cardInt <-
  df_mod2 %>%
    select(1, 3:96)

t1_start <- Sys.time()
mod_cardInt <- lm(leftstartingtrophies ~ (.)^2, data = df_cardInt) # all 2-way interactions (7 min)
t1_end <- Sys.time()
t1_end - t1_start

#summary(mod_cardInt)
#names(coef(mod_cardInt))[-1:-95]
```




## mod_cardInt_biglm: trophies ~ cards + all 2-way card interactions (biglm)
```{r}
df_cardInt <-
  df_mod2 %>%
    select(1, 3:96)

fInt <- as.formula(
  paste(
    "leftstartingtrophies ~ (",
    paste(
      paste("`", names(df_cardInt)[-1], "`", sep = ""),
      collapse = " + "
    ),
    ")^2"
  )
)

t1_start <- Sys.time()
mod_cardInt_biglm <- biglm::biglm(formula = fInt, data = df_cardInt)
#mod_cardInt_biglm <- biglm::biglm(leftstartingtrophies ~ (.)^2, data = df_cardInt)
t1_end <- Sys.time()
t1_end - t1_start # 4 min

#mod_cardInt_biglm$names[-1:-95]
```




## mod 2 v 2: trophies ~ day + card indicators + card numeric level + (card numeric level)^2 + card interactions
```{r}
f2 <- as.formula(
  paste(
    "leftstartingtrophies ~",
    paste(
      c(
        paste('`', names(df_mod2)[2:190], '`', sep = ''), # day + cards + levels
        paste('I(`', names(df_mod2)[97:190], '`^2)', sep = ''), # quadratic levels
        names(coef(mod_cardInt))[-1:-95] # all 2-way card interactions
        ),
      collapse = " + "
      )
    )
  )

t2_start <- Sys.time()
mod2v2 <- lm(formula = f2, data = df_mod2) # 7 min
t2_end <- Sys.time()
t2_end - t2_start

#summary(mod2v2)
tidy(mod2v2)
```




## mod 2 v 2 biglm: trophies ~ day + card indicators + card numeric level + (card numeric level)^2 + card interactions
```{r}
f2_biglm <- as.formula(
  paste(
    "leftstartingtrophies ~",
    paste(
      c(
        paste('`', names(df_mod2)[2:190], '`', sep = ''), # day + cards + levels
        paste('I(`', names(df_mod2)[97:190], '`^2)', sep = ''), # quadratic levels
        mod_cardInt_biglm$names[-1:-95] # all 2-way card interactions
        ),
      collapse = " + "
      )
    )
  )

t2_start <- Sys.time()
mod2v2_biglm <- biglm::biglm(formula = f2_biglm, data = df_mod2)
t2_end <- Sys.time()
t2_end - t2_start # 5 min

#summary(mod2v2_biglm)
tidy(mod2v2_biglm)
```









