---
title: "Bias Correction Idea"
output: html_document
---

## import model
```{r}
library(tidyverse)
library(mgcv)
# combined last active 4000+
# trophies ~ day + cards + lvl + lvl^2 + cardInt + day:lvl & lvl^2
lm <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2.rds")
```

## import df
```{r}
rarity <- read_csv("~/research/CR_Project_Tom/cr_rarity_level_adjustments.csv")

cr_cards <-
  jsonlite::fromJSON("~/research/CR_Project_Tom/clash_royale_card_info.json")$cards %>%
  select(name, rarity) %>%
  # season 1 added in Fisherman - nothing more up to season 3
  bind_rows(., tibble(name = "Fisherman", rarity = "Legendary")) %>%
  # season 4: elixir golem
  bind_rows(., tibble(name = "Elixir Golem", rarity = "Rare")) %>%
  # season 6: battle healer
  bind_rows(., tibble(name = "Battle Healer", rarity = "Rare")) %>%
  # season 7: firecracker
  bind_rows(., tibble(name = "Firecracker", rarity = "Common")) %>%
  # season 9: royal delivery
  bind_rows(., tibble(name = "Royal Delivery", rarity = "Common")) %>%
  # season 10: replaces heal with heal spirit
  mutate(name = str_replace(name, "^Heal$", "Heal Spirit"))

# reading in all lines
cr_full <- read_csv("~/research/CR_Project_Tom/data_by_season/clash_royale_matches_season_11_2020-05-04_to_2020-06-01.csv")



# combine left and right tags
df_left <- cr_full %>% select(1:7) %>% mutate()
names(df_left) <- c("id", "battletime", "arenaid",
                    "playertag", "startingtrophies", "trophychange", "deck")

df_right <- cr_full %>% select(1:3, 8:11)
names(df_right) <- c("id", "battletime", "arenaid",
                    "playertag", "startingtrophies", "trophychange", "deck")

df_combined <- bind_rows(df_left, df_right)



# filter only the active players based on playertag
cr_sub <-
  df_combined %>%
    group_by(playertag) %>%
    filter(n() >= 25) %>%
    arrange(desc(battletime)) %>%
    slice(1) %>% # only take the last match for a player
    ungroup() #187,234




# reduce vars
cr_reduced <-
  cr_sub %>%
  select(playertag, battletime, startingtrophies, trophychange, deck)


set.seed(3007)
cr <- cr_reduced %>%
  #filter(battletime > '2020-05-29') %>% # only look at the last few days in the season
  #sample_n(tbl = ., size = 20000) %>% # random sample of 20k
  filter(str_count(deck, pattern = ",") == 15) # ensures 8 card decks



# fix card/level part
xcards <-
cr %>%  
  separate_rows(deck, sep = "\\],") %>%
  separate(deck, into = c("Cards","Level"), sep = ", ") %>%
  mutate(Level = parse_number(Level),
         Cards = str_remove_all(Cards, "\\[+"),
         Cards = str_remove_all(Cards, '\\"'),
         Cards = str_trim(Cards, side = c("both"))
         ) %>%
  left_join(., cr_cards, by = c("Cards" = "name")) %>% # add rarity info
  left_join(rarity, by = "rarity") %>% # add level adjustment
  mutate(Level = Level  + level_adjustment) %>% # adjust levels
  select(-rarity, -level_adjustment, -trophychange) # reduce size of dataframe

x = model.matrix(~0 + Cards + Level, model.frame(~ ., xcards, na.action=na.pass)) # make indictor variables

#x = xcards %>%  model.matrix(~0 + Cards + Level, data = .) 

x = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")

colnames(x) = str_remove_all(colnames(x), "Cards")
colnames(x) = str_replace_all(colnames(x), " ", "_")
colnames(x) = str_replace_all(colnames(x), "-", "_")

# create names for all card and card interaction terms
interactions = labels(terms(~.^2, data = x[1:10,]))

colnames(x) = paste(colnames(x),"_Level",sep = "")

deck <- 
  x %>%
  as_tibble() %>%
  mutate(tmpid = xcards$playertag) %>%
  group_by(tmpid) %>%
  summarize_if(is.numeric, sum)

rm(x) # free up memory
rm(xcards)

# put back together
cr <- cr %>%
  select(battletime, startingtrophies) %>%
  bind_cols(sign(deck[,-1])) %>%
  bind_cols(deck[,-1])

rm(deck) # free memory from deck

names(cr) = str_remove_all(names(cr), "_Level") # fix anmes
names(cr) = str_replace_all(names(cr), "1","_Level") # one more fix



# filter 4000+ and convert battletime -> day of the month
cr <-
  cr %>%
  filter(startingtrophies >= 4000) %>%
  mutate(battletime = str_remove(battletime, "\\s.+")) %>%
  mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
  mutate(battletime = as.numeric(battletime))
```

## resid and pred
```{r}
df1 <- tibble(
  trophies = cr$startingtrophies,
  pred = predict.lm(lm, cr),
  resid = trophies - pred
)
```

## smoother model with GAM: resid ~ pred
```{r}
smooth <- gam(resid ~ s(pred), data = df1)
#saveRDS(smooth, "smooth.rds")
```

## predicted bias
```{r}
bias <- predict.gam(smooth, newdata = df1)
```

## adjusted prediction
```{r}
adjPred <- df1$pred - bias
```

## adjusted residuals vs actual trophies
```{r}
df2 <- tibble(
  trophies = cr$startingtrophies,
  adjPred = adjPred,
  adjResid = trophies - adjPred
)

df2 %>%
  ggplot(., aes(x = trophies, y = adjResid)) +
  geom_point() +
  geom_smooth() +
  theme_bw() +
  labs(
    title = "Residuals vs Trophies from Bias Correction"
  )
```

## compare with no adjustment
```{r}
df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  theme_bw() +
  labs(
    title = "Residuals vs Trophies without Bias Correction"
  )
```













# 2nd attempt

## fit model
```{r}
library(tidyverse)
library(mgcv)
# combined last active 4000+
# trophies ~ day + cards + lvl + lvl^2 + cardInt + day:lvl & lvl^2
t1 <- Sys.time()
lm <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2.rds")
t2 <- Sys.time()
t2 - t1
```

## round predictions to nearest 100
```{r}
predRounded <- round(lm$fitted.values / 100) * 100
```

## Calculate the above quantiles on the residuals for each “trophy group”
```{r}
dfQuant <- tibble(
  predRounded = predRounded,
  resid = lm$residuals
)

dfQuant <-
  dfQuant %>%
    group_by(predRounded) %>%
    summarise(
      resid05 = quantile(resid, probs = 0.05),
      resid25 = quantile(resid, probs = 0.25),
      resid50 = quantile(resid, probs = 0.50),
      resid75 = quantile(resid, probs = 0.75),
      resid95 = quantile(resid, probs = 0.95)
      )
```

## Given a new prediction from the model, adjust it by adding each of the five residual adjustments… map them to the tau idea from before
```{r}
adjPred <- tibble(
  trophies = lm$residuals + lm$fitted.values,
  pred = lm$fitted.values,
  predRounded = round(lm$fitted.values / 100) * 100
)

adjPred <-
  left_join(adjPred, dfQuant, by = "predRounded") %>%
    mutate(
      adjPred05 = pred + resid05,
      adjPred25 = pred + resid25,
      adjPred50 = pred + resid50,
      adjPred75 = pred + resid75,
      adjPred95 = pred + resid95,
      newResid05 = trophies - adjPred05, # for the plot
      newResid25 = trophies - adjPred25,
      newResid50 = trophies - adjPred50,
      newResid75 = trophies - adjPred75,
      newResid95 = trophies - adjPred95
    )
```

## residuals vs trophies
```{r}
# adjPred %>%
#   ggplot(., aes(x = trophies, y = newResid05)) +
#   geom_point() +
#   geom_smooth() +
#   labs(
#     title = "Residuals vs Trophies after 0.05 Quantile Adjustment"
#   )
```







# streamlined version for shiny app
```{r}
# strip model
# library(strip)
# lm <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2.rds")
# lmc <- strip(lm, keep = "predict")
# saveRDS(lmc, "~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2_strip.rds")

lm <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2_strip.rds")

# Calculate the quantiles on the residuals for each “trophy group”
dfQuant <- tibble(
  predRounded = round(lm$fitted.values / 100) * 100,
  resid = lm$residuals
) %>%
  group_by(predRounded) %>%
    summarise(
      resid05 = quantile(resid, probs = 0.05),
      resid25 = quantile(resid, probs = 0.25),
      resid50 = quantile(resid, probs = 0.50),
      resid75 = quantile(resid, probs = 0.75),
      resid95 = quantile(resid, probs = 0.95)
      )

# write_csv(dfQuant, "~/research/CR_Project_Tom/data_processed/residualAdj.csv")

# Given a new prediction from the model, adjust it by adding each of the five residual adjustments
adjPred <- tibble(
  pred = lm$fitted.values[[1]], # can be a prediction from newx
  predRounded = round(pred / 100) * 100
) %>%
  left_join(., dfQuant, by = "predRounded") %>%
    mutate(
      adjPred05 = pred + resid05,
      adjPred25 = pred + resid25,
      adjPred50 = pred + resid50,
      adjPred75 = pred + resid75,
      adjPred95 = pred + resid95
    ) %>%
  select(8:12) %>%
  round()
```

# plot
```{r}
adjPred1 <- adjPred
adjPred2 <- adjPred + 300

dfPlot <- tibble(
  prediction = c(as_vector(adjPred1), as_vector(adjPred2)),
  display = c(
    adjPred1[[1]] %/% 10,
    adjPred1[[2]] - adjPred1[[1]],
    adjPred1[[3]] - adjPred1[[2]],
    adjPred1[[4]] - adjPred1[[3]],
    adjPred1[[5]] - adjPred1[[4]],
    adjPred2[[1]] %/% 10,
    adjPred2[[2]] - adjPred2[[1]],
    adjPred2[[3]] - adjPred2[[2]],
    adjPred2[[4]] - adjPred2[[3]],
    adjPred2[[5]] - adjPred2[[4]]
  ),
  cumDisplay = c(
    cumsum(display[1:5]),
    cumsum(display[6:10])
  ),
  Percentile = paste(str_remove_all(c(names(adjPred1), names(adjPred2)), "[:alpha:]"), "th"),
  deck = c("Deck 1", "Deck 1", "Deck 1", "Deck 1", "Deck 1", "Deck 2", "Deck 2", "Deck 2", "Deck 2", "Deck 2")
)

dfPlot %>%
  ggplot(., aes(x = deck)) +
  geom_col(aes(y = display, fill = Percentile), width = 0.1, position = position_stack(reverse = T)) +
  geom_label(data = dfPlot[dfPlot$deck == "Deck 1", ], aes(y = cumDisplay, label = prediction, hjust = 1.5), size = 5) +
  geom_label(data = dfPlot[dfPlot$deck == "Deck 2", ], aes(y = cumDisplay, label = prediction, hjust = -0.5), size = 5) +
  theme_minimal() +
  scale_fill_viridis_d(option = "viridis") +
  guides(fill = guide_legend(reverse=TRUE)) +
  theme(
        legend.position = c(0.5, 0.25),
        legend.text = element_text(size = rel(1.2)),
        legend.title = element_text(size = rel(1.2)),
        line = element_blank(),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(
          color = "black",
          size = rel(1.5),
          vjust = 3
        ),
        plot.background = element_rect(fill = rgb(1,1,1,1))
      )
```








# streamlined version for shiny app - s12 updated
```{r}
# strip model
# library(strip)
# lm <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2.rds")
# lmc <- strip(lm, keep = "predict")
# saveRDS(lmc, "~/research/CR_Project_Tom/data_processed/mod_4000_s11_lm_2_strip.rds")

lm <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s12_lm_2.rds")

# Calculate the quantiles on the residuals for each “trophy group”
dfQuant <- tibble(
  predRounded = round(lm$fitted.values / 100) * 100,
  resid = lm$residuals
) %>%
  group_by(predRounded) %>%
    summarise(
      resid05 = quantile(resid, probs = 0.05),
      resid25 = quantile(resid, probs = 0.25),
      resid50 = quantile(resid, probs = 0.50),
      resid75 = quantile(resid, probs = 0.75),
      resid95 = quantile(resid, probs = 0.95)
      )

 write_csv(dfQuant, "~/residualAdj.csv")

# Given a new prediction from the model, adjust it by adding each of the five residual adjustments
adjPred <- tibble(
  pred = lm$fitted.values[[1]], # can be a prediction from newx
  predRounded = round(pred / 100) * 100
) %>%
  left_join(., dfQuant, by = "predRounded") %>%
    mutate(
      adjPred05 = pred + resid05,
      adjPred25 = pred + resid25,
      adjPred50 = pred + resid50,
      adjPred75 = pred + resid75,
      adjPred95 = pred + resid95
    ) %>%
  select(8:12) %>%
  round()
```

# plot
```{r}
adjPred1 <- adjPred
adjPred2 <- adjPred + 300

dfPlot <- tibble(
  prediction = c(as_vector(adjPred1), as_vector(adjPred2)),
  display = c(
    adjPred1[[1]] %/% 10,
    adjPred1[[2]] - adjPred1[[1]],
    adjPred1[[3]] - adjPred1[[2]],
    adjPred1[[4]] - adjPred1[[3]],
    adjPred1[[5]] - adjPred1[[4]],
    adjPred2[[1]] %/% 10,
    adjPred2[[2]] - adjPred2[[1]],
    adjPred2[[3]] - adjPred2[[2]],
    adjPred2[[4]] - adjPred2[[3]],
    adjPred2[[5]] - adjPred2[[4]]
  ),
  cumDisplay = c(
    cumsum(display[1:5]),
    cumsum(display[6:10])
  ),
  Percentile = paste(str_remove_all(c(names(adjPred1), names(adjPred2)), "[:alpha:]"), "th"),
  deck = c("Deck 1", "Deck 1", "Deck 1", "Deck 1", "Deck 1", "Deck 2", "Deck 2", "Deck 2", "Deck 2", "Deck 2")
)

dfPlot %>%
  ggplot(., aes(x = deck)) +
  geom_col(aes(y = display, fill = Percentile), width = 0.1, position = position_stack(reverse = T)) +
  geom_label(data = dfPlot[dfPlot$deck == "Deck 1", ], aes(y = cumDisplay, label = prediction, hjust = 1.5), size = 5) +
  geom_label(data = dfPlot[dfPlot$deck == "Deck 2", ], aes(y = cumDisplay, label = prediction, hjust = -0.5), size = 5) +
  theme_minimal() +
  scale_fill_viridis_d(option = "viridis") +
  guides(fill = guide_legend(reverse=TRUE)) +
  theme(
        legend.position = c(0.5, 0.25),
        legend.text = element_text(size = rel(1.2)),
        legend.title = element_text(size = rel(1.2)),
        line = element_blank(),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(
          color = "black",
          size = rel(1.5),
          vjust = 3
        ),
        plot.background = element_rect(fill = rgb(1,1,1,1))
      )
```













