---
title: "logit s11 winsor 42-63 eval"
output: html_document
---

## import mod1 and df1 - winsorized
```{r}
library(tidyverse)
library(quantreg)
logit_4360 <- readRDS("~/research/CR_Project_Tom/data_processed/logit_s11_winsor_43_60.rds")

cr <- read_csv("~/research/CR_Project_Tom/data_processed/logit_s11_data.csv")
# need filtering 4000+ and battletime conversion

# winsorize 6000+ = 6000
cr <- 
  cr %>%
    mutate(startingtrophies = if_else(startingtrophies > 6000, 6000, startingtrophies))

cr <-
  cr %>%
    filter(startingtrophies >= 4000) %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```




## predict trophies using win rate = 0.3
```{r}
df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_4360$coefficients
coefs[3] <- -0.3
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_4360$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActive Logit",
    subtitle = "win/lose ~ day + trophies + cards + levels (solve for trophies when win rate = 0.3)"
    ) +
  theme_bw()
```




## predict trophies using win rate = 0.4
```{r}
df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_4360$coefficients
coefs[3] <- -0.4
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_4360$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActive Logit",
    subtitle = "win/lose ~ day + trophies + cards + levels (solve for trophies when win rate = 0.4)"
    ) +
  theme_bw()
```




## predict trophies using win rate = 0.5
```{r}
df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_4360$coefficients
coefs[3] <- -0.5
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_4360$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActive Logit",
    subtitle = "win/lose ~ day + trophies + cards + levels (solve for trophies when win rate = 0.5)"
    ) +
  theme_bw()
```




## predict trophies using win rate = 0.6
```{r}
df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_4360$coefficients
coefs[3] <- -0.6
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_4360$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActive Logit",
    subtitle = "win/lose ~ day + trophies + cards + levels (solve for trophies when win rate = 0.6)"
    ) +
  theme_bw()
```




## predict trophies using win rate = 0.7
```{r}
df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_4360$coefficients
coefs[3] <- -0.7
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_4360$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActive Logit",
    subtitle = "win/lose ~ day + trophies + cards + levels (solve for trophies when win rate = 0.7)"
    ) +
  theme_bw()
```








# start over for mod2 df2 - no winsor

## import mod2 and df2
```{r}
library(tidyverse)
library(quantreg)
logit_noWinsor <- readRDS("~/research/CR_Project_Tom/data_processed/logit_s11_noWinsor.rds")

cr <- read_csv("~/research/CR_Project_Tom/data_processed/logit_s11_data.csv")
# need filtering 4000+ and battletime conversion

# winsorize 6000+ = 6000
# cr <- 
#   cr %>%
#     mutate(startingtrophies = if_else(startingtrophies > 6000, 6000, startingtrophies))

cr <-
  cr %>%
    filter(startingtrophies >= 4000) %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```




## predict trophies using win rate = 0.5
```{r}
df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_noWinsor$coefficients
coefs[3] <- -0.5
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_noWinsor$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: No Winsor S11 CombinedLastActive Logit",
    subtitle = "win/lose ~ day + trophies + cards + levels (solve for trophies when win rate = 0.5)"
    ) +
  theme_bw()
```








# start over for mod3 df3 - add in card interactions and quadratic levels

## import mod3 and df3
```{r}
library(tidyverse)
logit_intQuad <- readRDS("~/research/CR_Project_Tom/data_processed/logit_s11_winsor_43_60_int_quad.rds")

cr <- read_csv("~/research/CR_Project_Tom/data_processed/logit_s11_data.csv")
# need filtering 4000+ and battletime conversion

# winsorize 6000+ = 6000
cr <-
  cr %>%
    mutate(startingtrophies = if_else(startingtrophies > 6000, 6000, startingtrophies))

cr <-
  cr %>%
    filter(startingtrophies >= 4000) %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```




## predict trophies using win rate = 0.5
```{r}
lvl <- cr[,102:199]

lvlSq <- lvl^2

cards <- cr[,4:101]

cardInt <- model.matrix(~ .^2, data = cards)[,-1:-99]

df <-
cr %>%
  mutate(forInt = 1, forWinrate = 1, battletime = 30) %>%
  select(forInt, battletime, forWinrate, 4:199)

df <- bind_cols(df, lvlSq, as.data.frame(cardInt))

dfMat <- data.matrix(df)
dfMat <- t(dfMat)

coefs <- logit_intQuad$coefficients
coefs[3] <- -0.5
names(coefs) <- NULL

predMat <- coefs * dfMat
preds <- colSums(predMat, na.rm = T) * (-1 / logit_intQuad$coefficients[[3]])
```

## resid vs y plot
```{r}
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActive Logit",
    subtitle = "win ~ day + trophies + cards + lvl + lvl^2 + card interactions (solve for trophies when win rate = 0.5)"
    ) +
  theme_bw()
```






