---
title: "s1 models evaluation"
output: html_document
---

## import
```{r}
library(tidyverse)
```

```{r}
crL <- read_csv("~/research/CR_Project_Tom/data_processed/cr_s1_left.csv")
# process battle time -> day of the month
crL <-
  crL %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))

mod0 <- readRDS("~/research/CR_Project_Tom/data_processed/mod_0.rds")
mod4000 <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000.rds")
```


## right deck
```{r}
library(tidyverse)

rarity <- read_csv("~/research/CR_Project_Tom/cr_rarity_level_adjustments.csv")

cr_cards <-
  jsonlite::fromJSON("~/research/CR_Project_Tom/clash_royale_card_info.json")$cards %>%
  select(name, rarity) %>%
  # season 1 added in Fisherman
  bind_rows(., tibble(name = "Fisherman", rarity = "Legendary"))

# reading in 1,000,000 lines
cr <- read_csv("~/research/CR_Project_Tom/data_by_season/clash_royale_matches_season_1_2019-07-01_to_2019-08-05_right.csv", n_max = 105593) # 105594



# fix card/level part
x <-
cr %>%  
  mutate(rightdeck = str_remove_all(rightdeck, "[\\[\"]")) %>%
  separate_rows(rightdeck, sep = "\\], ") %>%
  separate(rightdeck, into = c("Cards","Level"), sep = ", ") %>%
  mutate(Level = parse_number(Level)) %>%
  left_join(., cr_cards, by = c("Cards" = "name")) %>% # add rarity info
  left_join(rarity, by = "rarity") %>% # add level adjustment
  mutate(Level = Level  + level_adjustment) %>% # adjust levels
  select(-rarity, -level_adjustment, -righttrophychange) %>% # reduce size of dataframe
  model.matrix(~0 + Cards + Level, data = .) # make indictor variables


x = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")

colnames(x) = str_remove_all(colnames(x), "Cards")
colnames(x) = str_replace_all(colnames(x), " ", "_")
colnames(x) = str_replace_all(colnames(x), "-", "_")

# create names for all card and card interaction terms
interactions = labels(terms(~.^2, data = x[1:10,]))

colnames(x) = paste(colnames(x),"_Level",sep = "")

deck <- 
  x %>%
  as_tibble() %>%
  mutate(tmpid = 1 + 0:(nrow(x)-1) %/% 8) %>%
  group_by(tmpid) %>%
  summarize_if(is.numeric, sum) %>%
  select(-tmpid)

rm(x) # free up memory from x

# put back together
cr <- cr %>%
  select(battletime, rightstartingtrophies) %>%
  bind_cols(sign(deck)) %>%
  bind_cols(deck)

rm(deck) # free memory from deck

names(cr) = str_remove_all(names(cr), "_Level") # fix anmes
names(cr) = str_replace_all(names(cr), "1","_Level") # one more fix

crR <- cr

crR <-
  crR %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```




## <4000 model
```{r}
rightPreds <- predict(mod0, crR[1:100000,])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = rightPreds)
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod0, crL[1:100000,])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = leftPreds)
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(title = "Residuals vs Trophies (S1) Using Low-Trophies (<4000) S1 Model") +
  theme_bw()
```


## 4000+ model
```{r}
rightPreds <- predict(mod4000, crR[1:100000,])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = rightPreds)
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod4000, crL[1:100000,])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = leftPreds)
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(title = "Residuals vs Trophies (S1) Using Arena 13 (4000+ Trophies) S1 Model") +
  theme_bw()


# for final presentation
dfL %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    x = "Trophies",
    y = "Residuals",
    title = "Residuals vs Trophies Using Full Model"
  ) +
  theme_bw()
```




# season 2 datasets

## left deck
```{r}
library(tidyverse)

rarity <- read_csv("~/research/CR_Project_Tom/cr_rarity_level_adjustments.csv")

cr_cards <-
  jsonlite::fromJSON("~/research/CR_Project_Tom/clash_royale_card_info.json")$cards %>%
  select(name, rarity) %>%
  # season 1 added in Fisherman
  bind_rows(., tibble(name = "Fisherman", rarity = "Legendary"))

# reading in 1,000,000 lines
cr <- read_csv("~/research/CR_Project_Tom/data_by_season/clash_royale_matches_season_2_2019-08-05_to_2019-09-02_left.csv", n_max = 100000)



# fix card/level part
x <-
cr %>%  
  mutate(leftdeck = str_remove_all(leftdeck, "[\\[\"]")) %>%
  separate_rows(leftdeck, sep = "\\], ") %>%
  separate(leftdeck, into = c("Cards","Level"), sep = ", ") %>%
  mutate(Level = parse_number(Level)) %>%
  left_join(., cr_cards, by = c("Cards" = "name")) %>% # add rarity info
  left_join(rarity, by = "rarity") %>% # add level adjustment
  mutate(Level = Level  + level_adjustment) %>% # adjust levels
  select(-rarity, -level_adjustment, -lefttrophychange) %>% # reduce size of dataframe
  model.matrix(~0 + Cards + Level, data = .) # make indictor variables


x = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")

colnames(x) = str_remove_all(colnames(x), "Cards")
colnames(x) = str_replace_all(colnames(x), " ", "_")
colnames(x) = str_replace_all(colnames(x), "-", "_")

# create names for all card and card interaction terms
interactions = labels(terms(~.^2, data = x[1:10,]))

colnames(x) = paste(colnames(x),"_Level",sep = "")

deck <- 
  x %>%
  as_tibble() %>%
  mutate(tmpid = 1 + 0:(nrow(x)-1) %/% 8) %>%
  group_by(tmpid) %>%
  summarize_if(is.numeric, sum) %>%
  select(-tmpid)

rm(x) # free up memory from x

# put back together
cr <- cr %>%
  select(battletime, leftstartingtrophies) %>%
  bind_cols(sign(deck)) %>%
  bind_cols(deck)

rm(deck) # free memory from deck

names(cr) = str_remove_all(names(cr), "_Level") # fix anmes
names(cr) = str_replace_all(names(cr), "1","_Level") # one more fix

crL <- cr

crL <-
  crL %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```


## right deck
```{r}
library(tidyverse)

rarity <- read_csv("~/research/CR_Project_Tom/cr_rarity_level_adjustments.csv")

cr_cards <-
  jsonlite::fromJSON("~/research/CR_Project_Tom/clash_royale_card_info.json")$cards %>%
  select(name, rarity) %>%
  # season 1 added in Fisherman
  bind_rows(., tibble(name = "Fisherman", rarity = "Legendary"))

# reading in 1,000,000 lines
cr <- read_csv("~/research/CR_Project_Tom/data_by_season/clash_royale_matches_season_2_2019-08-05_to_2019-09-02_right.csv", n_max = 100000)



# fix card/level part
x <-
cr %>%  
  mutate(rightdeck = str_remove_all(rightdeck, "[\\[\"]")) %>%
  separate_rows(rightdeck, sep = "\\], ") %>%
  separate(rightdeck, into = c("Cards","Level"), sep = ", ") %>%
  mutate(Level = parse_number(Level)) %>%
  left_join(., cr_cards, by = c("Cards" = "name")) %>% # add rarity info
  left_join(rarity, by = "rarity") %>% # add level adjustment
  mutate(Level = Level  + level_adjustment) %>% # adjust levels
  select(-rarity, -level_adjustment, -righttrophychange) %>% # reduce size of dataframe
  model.matrix(~0 + Cards + Level, data = .) # make indictor variables


x = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")

colnames(x) = str_remove_all(colnames(x), "Cards")
colnames(x) = str_replace_all(colnames(x), " ", "_")
colnames(x) = str_replace_all(colnames(x), "-", "_")

# create names for all card and card interaction terms
interactions = labels(terms(~.^2, data = x[1:10,]))

colnames(x) = paste(colnames(x),"_Level",sep = "")

deck <- 
  x %>%
  as_tibble() %>%
  mutate(tmpid = 1 + 0:(nrow(x)-1) %/% 8) %>%
  group_by(tmpid) %>%
  summarize_if(is.numeric, sum) %>%
  select(-tmpid)

rm(x) # free up memory from x

# put back together
cr <- cr %>%
  select(battletime, rightstartingtrophies) %>%
  bind_cols(sign(deck)) %>%
  bind_cols(deck)

rm(deck) # free memory from deck

names(cr) = str_remove_all(names(cr), "_Level") # fix anmes
names(cr) = str_replace_all(names(cr), "1","_Level") # one more fix

crR <- cr

crR <-
  crR %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```


## <4000 model
```{r}
rightPreds <- predict(mod0, crR[1:100000,])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = rightPreds)
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod0, crL[1:100000,])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = leftPreds)
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(title = "Residuals vs Trophies (S2) Using Low-Trophies (<4000) S1 Model") +
  theme_bw()
```


## 4000+ model
```{r}
rightPreds <- predict(mod4000, crR[1:100000,])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = rightPreds)
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod4000, crL[1:100000,])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = leftPreds)
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(title = "Residuals vs Trophies (S2) Using Arena 13 (4000+ Trophies) S1 Model") +
  theme_bw()
```





