---
title: "Season 3 model evaluation"
output: html_document
---

## import models
```{r}
library(tidyverse)

mod0s3 <- readRDS("~/research/CR_Project_Tom/data_processed/mod_0_s3.rds")
mod4000s3 <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_s3.rds")
mod0logs3 <- readRDS("~/research/CR_Project_Tom/data_processed/mod_0_log_s3.rds")
mod4000logs3 <- readRDS("~/research/CR_Project_Tom/data_processed/mod_4000_log_s3.rds")

```


## import s3 left
```{r}
rarity <- read_csv("~/research/CR_Project_Tom/cr_rarity_level_adjustments.csv")

cr_cards <-
  jsonlite::fromJSON("~/research/CR_Project_Tom/clash_royale_card_info.json")$cards %>%
  select(name, rarity) %>%
  # season 1 added in Fisherman - nothing more up to season 3
  bind_rows(., tibble(name = "Fisherman", rarity = "Legendary"))

# reading in all lines
cr_full <- read_csv("~/research/CR_Project_Tom/data_by_season/clash_royale_matches_season_3_2019-09-02_to_2019-10-07_left.csv")


set.seed(3007)
cr <- cr_full %>%
#  filter(battletime > '2019-08-02') %>%
  sample_n(tbl = ., size = 1000000) %>% # random sample of 1 mil
  filter(str_count(leftdeck, pattern = ",") == 15) # ensures 8 card decks


# fix card/level part
xcards <-
cr %>%  
  separate_rows(leftdeck, sep = "\\],") %>%
  separate(leftdeck, into = c("Cards","Level"), sep = ", ") %>%
  mutate(Level = parse_number(Level),
         Cards = str_remove_all(Cards, "\\[+"),
         Cards = str_remove_all(Cards, '\\"'),
         Cards = str_trim(Cards, side = c("both"))
         ) %>%
  left_join(., cr_cards, by = c("Cards" = "name")) %>% # add rarity info
  left_join(rarity, by = "rarity") %>% # add level adjustment
  mutate(Level = Level  + level_adjustment) %>% # adjust levels
  select(-rarity, -level_adjustment, -lefttrophychange) # reduce size of dataframe

x = model.matrix(~0 + Cards + Level, model.frame(~ ., xcards, na.action=na.pass)) # make indictor variables

#x = xcards %>%  model.matrix(~0 + Cards + Level, data = .) 

x = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")

colnames(x) = str_remove_all(colnames(x), "Cards")
colnames(x) = str_replace_all(colnames(x), " ", "_")
colnames(x) = str_replace_all(colnames(x), "-", "_")

# create names for all card and card interaction terms
interactions = labels(terms(~.^2, data = x[1:10,]))

colnames(x) = paste(colnames(x),"_Level",sep = "")

deck <- 
  x %>%
  as_tibble() %>%
  mutate(tmpid = xcards$id) %>%
  group_by(tmpid) %>%
  summarize_if(is.numeric, sum)

rm(x) # free up memory
rm(xcards)

# put back together
cr <- cr %>%
  select(battletime, leftstartingtrophies) %>%
  bind_cols(sign(deck[,-1])) %>%
  bind_cols(deck[,-1])

rm(deck) # free memory from deck

names(cr) = str_remove_all(names(cr), "_Level") # fix anmes
names(cr) = str_replace_all(names(cr), "1","_Level") # one more fix



# convert battletime -> day of the month
crL <-
  cr %>%
  mutate(battletime = str_remove(battletime, "\\s.+")) %>%
  mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
  mutate(battletime = as.numeric(battletime))
```


## import s3 right
```{r}
rarity <- read_csv("~/research/CR_Project_Tom/cr_rarity_level_adjustments.csv")

cr_cards <-
  jsonlite::fromJSON("~/research/CR_Project_Tom/clash_royale_card_info.json")$cards %>%
  select(name, rarity) %>%
  # season 1 added in Fisherman - nothing more up to season 3
  bind_rows(., tibble(name = "Fisherman", rarity = "Legendary"))

# reading in all lines
cr_full <- read_csv("~/research/CR_Project_Tom/data_by_season/clash_royale_matches_season_3_2019-09-02_to_2019-10-07_right.csv")


set.seed(3007)
cr <- cr_full %>%
#  filter(battletime > '2019-08-02') %>%
  sample_n(tbl = ., size = 1000000) %>% # random sample of 1 mil
  filter(str_count(rightdeck, pattern = ",") == 15) # ensures 8 card decks


# fix card/level part
xcards <-
cr %>%  
  separate_rows(rightdeck, sep = "\\],") %>%
  separate(rightdeck, into = c("Cards","Level"), sep = ", ") %>%
  mutate(Level = parse_number(Level),
         Cards = str_remove_all(Cards, "\\[+"),
         Cards = str_remove_all(Cards, '\\"'),
         Cards = str_trim(Cards, side = c("both"))
         ) %>%
  left_join(., cr_cards, by = c("Cards" = "name")) %>% # add rarity info
  left_join(rarity, by = "rarity") %>% # add level adjustment
  mutate(Level = Level  + level_adjustment) %>% # adjust levels
  select(-rarity, -level_adjustment, -righttrophychange) # reduce size of dataframe

x = model.matrix(~0 + Cards + Level, model.frame(~ ., xcards, na.action=na.pass)) # make indictor variables

#x = xcards %>%  model.matrix(~0 + Cards + Level, data = .) 

x = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")

colnames(x) = str_remove_all(colnames(x), "Cards")
colnames(x) = str_replace_all(colnames(x), " ", "_")
colnames(x) = str_replace_all(colnames(x), "-", "_")

# create names for all card and card interaction terms
interactions = labels(terms(~.^2, data = x[1:10,]))

colnames(x) = paste(colnames(x),"_Level",sep = "")

deck <- 
  x %>%
  as_tibble() %>%
  mutate(tmpid = xcards$id) %>%
  group_by(tmpid) %>%
  summarize_if(is.numeric, sum)

rm(x) # free up memory
rm(xcards)

# put back together
cr <- cr %>%
  select(battletime, rightstartingtrophies) %>%
  bind_cols(sign(deck[,-1])) %>%
  bind_cols(deck[,-1])

rm(deck) # free memory from deck

names(cr) = str_remove_all(names(cr), "_Level") # fix anmes
names(cr) = str_replace_all(names(cr), "1","_Level") # one more fix



# convert battletime -> day of the month
crR <-
  cr %>%
  mutate(battletime = str_remove(battletime, "\\s.+")) %>%
  mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
  mutate(battletime = as.numeric(battletime))
```


# predict season 3

## <4000 full model
```{r}
# trophies ~ cards + levels + levels^2 + card interactions

rightPreds <- predict(mod0s3, crR[1:100000,])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = rightPreds)
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod0s3, crL[1:100000,])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = leftPreds)
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(
    title = "Residuals vs Trophies (S3) Using Low-Trophies (<4000) S3 Full Model",
    subtitle = "trophies ~ cards + levels + levels^2 + card interactions"
    ) +
  theme_bw()
```


## 4000+ model
```{r}
# trophies ~ dayOfTheMonth + cards + levels + levels^2 + card interactions

rightPreds <- predict(mod4000s3, crR[1:100000,-2])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = rightPreds)
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod4000s3, crL[1:100000,-2])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = leftPreds)
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(
    title = "Residuals vs Trophies (S3) Using Arena 13 (4000+ Trophies) S3 Full Model",
    subtitle = "trophies ~ dayOfTheMonth + cards + levels + levels^2 + card interactions"
    ) +
  theme_bw()
```


## <4000 log model
```{r}
# log(trophies) ~ cards + levels + card interactions

rightPreds <- predict(mod0logs3, crR[1:100000,])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = exp(rightPreds))
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod0logs3, crL[1:100000,])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = exp(leftPreds))
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(
    title = "Residuals vs Trophies (S3) Using Low-Trophies (<4000) S3 Log Model",
    subtitle = "log(trophies) ~ cards + levels + card interactions"
    ) +
  theme_bw()
```


## 4000+ log model
```{r}
# log(trophies) ~ dayOfTheMonth + cards + levels + card interactions

rightPreds <- predict(mod4000logs3, crR[1:100000,-2])
dfR <- tibble(trophies = crR$rightstartingtrophies[1:100000], preds = exp(rightPreds))
dfR <-
  dfR %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "right")

leftPreds <- predict(mod4000logs3, crL[1:100000,-2])
dfL <- tibble(trophies = crL$leftstartingtrophies[1:100000], preds = exp(leftPreds))
dfL <-
  dfL %>%
  mutate(resid = trophies - preds) %>%
  mutate(group = "left")

df1 <- bind_rows(dfR, dfL)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point(aes(color = group)) +
  geom_smooth(aes(linetype = group)) +
  labs(
    title = "Residuals vs Trophies (S3) Using Arena 13 (4000+ Trophies) S3 Log Model",
    subtitle = "log(trophies) ~ dayOfTheMonth + cards + levels + card interactions"
    ) +
  theme_bw()
```











