---
title: "s11 eval"
output: html_document
---

## import quantmod df
```{r}
library(tidyverse)
library(quantreg)
cr <- read_csv("~/research/CR_Project_Tom/data_processed/quantmod_s11_data.csv")
# need filtering 4000+ and battletime conversion
```

## filtering and conversion
```{r}
cr <-
  cr %>%
  filter(startingtrophies >= 4001 & startingtrophies < 6600) %>%
  mutate(battletime = str_remove(battletime, "\\s.+")) %>%
  mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
  mutate(battletime = as.numeric(battletime))
```







## mod1: quantmod_s11_75
** trophies ~ battletime (day) + cards + lvl + lvl^2 + battletime:lvl & lvl^2 **
```{r}
# build formula
quad_level_terms = cr %>%
  names() %>%
  str_detect(., pattern = "Level") %>%
  which() %>%
  names(cr)[.] %>%
  paste("I(",., "^2)", sep = "")

f <-
  as.formula(
    paste(
      paste("startingtrophies ~ "), # response
      paste(names(cr)[-2], collapse =  " + "), " + ", #  battletime and  first level vars
      #paste(names(cr)[-(1:2)], collapse =  " + "), " + ", # no battletime and yes first level vars
      paste(quad_level_terms, collapse =  " + "), " + ", # quadratic level vars
      #paste(interactions[-1:-98], collapse = " + "), " + ",
      paste("battletime:", c(names(cr)[101:198], quad_level_terms), sep = "", collapse = " + ") # battle interact with levels and levels^2
    )
  )


# fit model
quantmod_s11_75 <- rq(
  formula = f, data = cr, tau = 0.75, method = "sfn",
  control = list(tmpmax= dim(cr)[2]*600)
  )
```


## mod1 resid vs y plot
```{r}
preds <- predict(quantmod_s11_75, cr[,-2])
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4001-6600 S11 CombinedLastActiveWin 0.75 QuantMod",
    subtitle = "trophies ~ dayOfTheMonth + cards + levels + levels^2 + day:lvl & lvl^2"
    ) +
  theme_bw()
```


## trophy-lvl investigation (violin)
```{r}
# for end of season matches
# calculate average level per deck, rounded to nearest 0.25
levels <- cr[, 101:198]

avgLvlPerDeck <-
  levels %>%
    transmute(total = rowSums(levels)) %>%
    transmute(avg = total/8) %>%
    mutate(avg = round(avg / 0.25) * 0.25)
```

```{r}
df2 <-
  bind_cols(cr[,2], avgLvlPerDeck) %>%
    arrange(avg)

df2$avg <- factor(df2$avg)
df2$avg <- fct_inorder(df2$avg)

df2 %>%
  ggplot(., aes(x = avg, y = startingtrophies)) +
  geom_violin() +
  labs(
    x = "Average Card Level per Deck",
    y = "Trophies",
    title = "Violin Plot of Trophies vs Average Card Level for Last Active S11 Win"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      vjust = 0.5,
      face = "bold"    
      )
  )
```


## quantile regression (geom)
```{r}
df3 <-
  bind_cols(cr[,2], avgLvlPerDeck) %>%
    arrange(avg)

df3 %>%
  ggplot(., aes(x = avg, y = startingtrophies)) +
  geom_point() +
  geom_quantile(
    quantiles = 0.95,
    method = "rq",
    color = "blue"
  ) +
  geom_quantile(
    quantiles = 0.95,
    method = "rqss",
    color = "red"
  ) +
  labs(
    x = "Average Card Level per Deck",
    y = "Trophies",
    title = "Quantile Regression for Trophies vs Average Card Level (Last Active S11 Win)",
    subtitle = "Blue = rq, Red = rqss"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      vjust = 0.5,
      face = "bold"    
      )
  )
```







## mod2: quantmod_s11_75_noquad
** trophies ~ battletime (day) + cards + lvl + battletime:lvl **
```{r}
# build formula
quad_level_terms = cr %>%
  names() %>%
  str_detect(., pattern = "Level") %>%
  which() %>%
  names(cr)[.] %>%
  paste("I(",., "^2)", sep = "")

f <-
  as.formula(
    paste(
      paste("startingtrophies ~ "), # response
      paste(names(cr)[-2], collapse =  " + "), " + ", #  battletime and  first level vars
      #paste(names(cr)[-(1:2)], collapse =  " + "), " + ", # no battletime and yes first level vars
      #paste(quad_level_terms, collapse =  " + "), " + ", # quadratic level vars
      #paste(interactions[-1:-98], collapse = " + "), " + ",
      paste("battletime:", names(cr)[101:198], collapse = " + ") # battle interact with levels
    )
  )


# fit model
quantmod_s11_75_noquad <- rq(
  formula = f, data = cr, tau = 0.75, method = "sfn",
  control = list(tmpmax= dim(cr)[2]*600)
  )
```


## mod2 resid vs y plot
```{r}
preds <- predict(quantmod_s11_75_noquad, cr[,-2])
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4001-6600 S11 CombinedLastActiveWin 0.75 QuantMod noQuad",
    subtitle = "trophies ~ dayOfTheMonth + cards + levels + day:lvl"
    ) +
  theme_bw()
```







## mod3: quantmod_s11_50
** trophies ~ battletime (day) + cards + lvl + lvl^2 + battletime:lvl & lvl^2 **
```{r}
# build formula
quad_level_terms = cr %>%
  names() %>%
  str_detect(., pattern = "Level") %>%
  which() %>%
  names(cr)[.] %>%
  paste("I(",., "^2)", sep = "")

f <-
  as.formula(
    paste(
      paste("startingtrophies ~ "), # response
      paste(names(cr)[-2], collapse =  " + "), " + ", #  battletime and  first level vars
      #paste(names(cr)[-(1:2)], collapse =  " + "), " + ", # no battletime and yes first level vars
      paste(quad_level_terms, collapse =  " + "), " + ", # quadratic level vars
      #paste(interactions[-1:-98], collapse = " + "), " + ",
      paste("battletime:", c(names(cr)[101:198], quad_level_terms), sep = "", collapse = " + ") # battle interact with levels and levels^2
    )
  )


# fit model
quantmod_s11_50 <- rq(
  formula = f, data = cr, tau = 0.50, method = "sfn",
  control = list(tmpmax= dim(cr)[2]*600)
  )
```


## mod1 resid vs y plot
```{r}
preds <- predict(quantmod_s11_50, cr[,-2])
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4001-6600 S11 CombinedLastActiveWin 0.50 QuantMod",
    subtitle = "trophies ~ dayOfTheMonth + cards + levels + levels^2 + day:lvl & lvl^2"
    ) +
  theme_bw()
```








## mod4: quantmod_s11_95
** trophies ~ battletime (day) + cards + lvl + lvl^2 + battletime:lvl & lvl^2 **
```{r}
# build formula
quad_level_terms = cr %>%
  names() %>%
  str_detect(., pattern = "Level") %>%
  which() %>%
  names(cr)[.] %>%
  paste("I(",., "^2)", sep = "")

f <-
  as.formula(
    paste(
      paste("startingtrophies ~ "), # response
      paste(names(cr)[-2], collapse =  " + "), " + ", #  battletime and  first level vars
      #paste(names(cr)[-(1:2)], collapse =  " + "), " + ", # no battletime and yes first level vars
      paste(quad_level_terms, collapse =  " + "), " + ", # quadratic level vars
      #paste(interactions[-1:-98], collapse = " + "), " + ",
      paste("battletime:", c(names(cr)[101:198], quad_level_terms), sep = "", collapse = " + ") # battle interact with levels and levels^2
    )
  )


# fit model
quantmod_s11_95 <- rq(
  formula = f, data = cr, tau = 0.95, method = "sfn",
  control = list(tmpmax= dim(cr)[2]*600)
  )
```


## mod1 resid vs y plot
```{r}
preds <- predict(quantmod_s11_95, cr[,-2])
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4001-6600 S11 CombinedLastActiveWin 0.95 QuantMod",
    subtitle = "trophies ~ dayOfTheMonth + cards + levels + levels^2 + day:lvl & lvl^2"
    ) +
  theme_bw()
```








## mod4: quantmod_s11_25
** trophies ~ battletime (day) + cards + lvl + lvl^2 + battletime:lvl & lvl^2 **
```{r}
# build formula
quad_level_terms = cr %>%
  names() %>%
  str_detect(., pattern = "Level") %>%
  which() %>%
  names(cr)[.] %>%
  paste("I(",., "^2)", sep = "")

f <-
  as.formula(
    paste(
      paste("startingtrophies ~ "), # response
      paste(names(cr)[-2], collapse =  " + "), " + ", #  battletime and  first level vars
      #paste(names(cr)[-(1:2)], collapse =  " + "), " + ", # no battletime and yes first level vars
      paste(quad_level_terms, collapse =  " + "), " + ", # quadratic level vars
      #paste(interactions[-1:-98], collapse = " + "), " + ",
      paste("battletime:", c(names(cr)[101:198], quad_level_terms), sep = "", collapse = " + ") # battle interact with levels and levels^2
    )
  )


# fit model
quantmod_s11_25 <- rq(
  formula = f, data = cr, tau = 0.25, method = "sfn",
  control = list(tmpmax= dim(cr)[2]*600)
  )
```


## mod1 resid vs y plot
```{r}
preds <- predict(quantmod_s11_25, cr[,-2])
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4001-6600 S11 CombinedLastActiveWin 0.25 QuantMod",
    subtitle = "trophies ~ dayOfTheMonth + cards + levels + levels^2 + day:lvl & lvl^2"
    ) +
  theme_bw()
```













