---
title: "rq s11 winsor 42-63 eval"
output: html_document
---

## import mod and df
```{r}
library(tidyverse)
library(quantreg)
winsor_4263 <- readRDS("~/research/CR_Project_Tom/data_processed/rq_s11_winsor_42_63.rds")

cr <- read_csv("~/research/CR_Project_Tom/data_processed/quantmod_s11_data.csv")
# need filtering 4000+ and battletime conversion

# winsorize 6300+
cr <- 
  cr %>%
    mutate(startingtrophies = if_else(startingtrophies > 6300, 6300, startingtrophies))
```

## filtering and conversion
```{r}
cr <-
  cr %>%
  filter(startingtrophies >= 4200 & startingtrophies < 6300) %>%
  mutate(battletime = str_remove(battletime, "\\s.+")) %>%
  mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
  mutate(battletime = as.numeric(battletime))
```

## prediction matrix
```{r}
predsMat <- predict.rq(winsor_4263, cr)
```




## rq25 resid vs y plot
```{r}
preds <- predsMat[,1] # tau = 0.25
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4200-6300 Winsor S11 CombinedLastActiveWin rq 0.25",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## rq50 resid vs y plot
```{r}
preds <- predsMat[,2] # tau = 0.50
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4200-6300 Winsor S11 CombinedLastActiveWin rq 0.50",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## rq75 resid vs y plot
```{r}
preds <- predsMat[,3] # tau = 0.75
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4200-6300 Winsor S11 CombinedLastActiveWin rq 0.75",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## rq95 resid vs y plot
```{r}
preds <- predsMat[,4] # tau = 0.95
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4200-6300 Winsor S11 CombinedLastActiveWin rq 0.95",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```










# start over from line 1 for second winsor model

## import mod2 and df2
```{r}
library(tidyverse)
library(quantreg)
winsor_4360 <- readRDS("~/research/CR_Project_Tom/data_processed/rq_s11_winsor_43_60.rds")

cr <- read_csv("~/research/CR_Project_Tom/data_processed/quantmod_s11_data.csv")
# need filtering 4000+ and battletime conversion

# winsorize 6000+ = 6000
cr <- 
  cr %>%
    mutate(startingtrophies = if_else(startingtrophies > 6000, 6000, startingtrophies))

cr <-
  cr %>%
    filter(startingtrophies >= 4000) %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```

## prediction matrix
```{r}
predsMat2 <- predict.rq(winsor_4360, cr)
```




## winsor 2 - rq25 resid vs y plot
```{r}
preds <- predsMat2[,1] # tau = 0.25
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.25",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 2 - rq50 resid vs y plot
```{r}
preds <- predsMat2[,2] # tau = 0.50
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.50",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 2 - rq75 resid vs y plot
```{r}
preds <- predsMat2[,3] # tau = 0.75
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.75",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 2 - rq95 resid vs y plot
```{r}
preds <- predsMat2[,4] # tau = 0.95
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.95",
    subtitle = "trophies ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```















# start over for third winsor log model

## import mod3 and df3
```{r}
library(tidyverse)
library(quantreg)
winsor_4360_log <- readRDS("~/research/CR_Project_Tom/data_processed/rq_s11_winsor_43_60_log.rds")

cr <- read_csv("~/research/CR_Project_Tom/data_processed/quantmod_s11_data.csv")
# need filtering 4000+ and battletime conversion

# winsorize 6000+ = 6000
cr <- 
  cr %>%
    mutate(startingtrophies = if_else(startingtrophies > 6000, 6000, startingtrophies))

cr <-
  cr %>%
    filter(startingtrophies >= 4000) %>%
    mutate(battletime = str_remove(battletime, "\\s.+")) %>%
    mutate(battletime = str_remove(battletime, "[:digit:]{4}-[:digit:]{2}-")) %>%
    mutate(battletime = as.numeric(battletime))
```

## prediction matrix
```{r}
predsMat3 <- exp(predict.rq(winsor_4360_log, cr))
```




## winsor 3 - rq05 resid vs y plot
```{r}
preds <- predsMat3[,1] # tau = 0.05
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.05",
    subtitle = "log(trophies) ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 3 - rq10 resid vs y plot
```{r}
preds <- predsMat3[,2] # tau = 0.10
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.10",
    subtitle = "log(trophies) ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 3 - rq25 resid vs y plot
```{r}
preds <- predsMat3[,3] # tau = 0.25
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.25",
    subtitle = "log(trophies) ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 3 - rq50 resid vs y plot
```{r}
preds <- predsMat3[,4] # tau = 0.50
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.50",
    subtitle = "log(trophies) ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 3 - rq75 resid vs y plot
```{r}
preds <- predsMat3[,5] # tau = 0.75
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.75",
    subtitle = "log(trophies) ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```




## winsor 3 - rq95 resid vs y plot
```{r}
preds <- predsMat3[,6] # tau = 0.95
df1 <- tibble(trophies = cr$startingtrophies, preds = preds)
df1 <-
  df1 %>%
  mutate(resid = trophies - preds)

df1 %>%
  ggplot(., aes(x = trophies, y = resid)) +
  geom_point() +
  geom_smooth() +
  labs(
    title = "Residual vs Trophy: 4300-6000 Winsor S11 CombinedLastActiveWin rq 0.95",
    subtitle = "log(trophies) ~ dayOfTheMonth + levels"
    ) +
  theme_bw()
```





